# Introduction

  Biological samples of British Columbia (BC) sablefish (*Anoplopoma fimbria*) from trap and hook & line fisheries have been collected from a fishery-based voluntary catch sampling program since 1995 [@Haist2001].  Prior to 2018, samples of whole fish were collected dockside by Fisheries and Oceans Canada (DFO) port samplers and/or contracted service providers via the dockside monitoring program (DMP). In addition, tagged fish were collected whole from commercial fisheries (trap, trawl, hook & line) at the point of landing, also by the dockside monitoring program. Biological data collected during catch sampling included fork length and sex. Otoliths were collected and archived for future ageing analyses.  These data provide a fishery-dependent source of age and size composition data for the two-sex age structured operating model used as part of the BC Management Strategy Evaluation (MSE) [@Cox2019, DFO 2020].

  Between 2016 and 2017, DFO undertook research to evaluate the potential change to a 'head only' catch sampling program for sablefish trap and hook & line fisheries.  Head only sampling allows commercial crew to collect samples directly while at sea, thereby eliminating the need to rely on port samplers for dockside data collection as well as the need for fishing vessels to store whole fish. Instead, commercial crew J-cut the fish at-sea as per commercial practice, examine the gonads to determine sex, mark the sex with knife cuts on the operculum, and store the frozen head (and/or floy tag) for later sampling by science personal. The key motivation for switching to a head only sampling program was to increase the number and spatial distribution of fishery samples, while simultaneously maintaining the quality of biological data.

  Evaluating the potential success of a head only sampling program for sablefish required the development and testing of new methods. First, a method was required to estimate sablefish fork length from head samples. Previous research on other fish species has shown that lengths can be accurately estimated from head dimensions [@Serafy1996; @Park2007], head and mandible lengths [@Isermann2005], and head height to eye diameter ratio [@Richardson2015], so we considered six different cranial measurement linked to these as a starting point for sablefish.  Second, the accuracy of methods used by commercial fishing crew to identify and record sex needed to be assessed, which required the development of DNA analysis techniques for sablefish gender detection.

  In this technical report, we describe a research investigation in 2016 that collected sablefish samples to: 1) identify cranial measurements that are reliable predictors of fork length for Sablefish; 2) identify cranial measurements that are practical to measure; and 3) develop DNA analysis techniques for gender detection.  We also describe the fishery pilot study in 2017 to: 1) assess the ease of sample collection for commercial fishers; 2) determine the accuracy of fisher sex identification using DNA analysis; followed by 3) among-sampler measurements of each head morphometric.
  
  

```{r sampleCount} 

    pointdata    <-  read.csv(paste(path,'figure1.csv',sep=''),header=T)  # read from csv
    females      <-  pointdata[pointdata$SPECIMEN_SEX_DESC=='FEMALE',]
    males        <-  pointdata[pointdata$SPECIMEN_SEX_DESC=='MALE',]

```
  

```{r words_surplus}   

#ORDER OF EVENTS:
#1. 2016 sample sablefish on research surveys, collect bio data and DNA
#2. 2016 head measurements on shore PBS lab, evaluate measurements with 5 point scale
#3. 2016 develop dna sex id by PBS Molecular Genetics Lab
#4. 2017 collect head samples on commercial vessel FOS TRIP 338773  Pacific Viking
#5  2017 measure head samples with 3 samplers to develop Index of Average Error
#6. 2017 use DNA to determine fisher sex accuracy

#The at-sea #observer program (ASOP) also collected biological data from the partial at-sea observer coverage (10% of sea days) on commercial trips from 2001 # through to 2005 [@IFMP2001], [@IFMP2004]. 

#In addition, biological samples have been processed by at-sea observers from the offshore seamount fishery that began as an experimental fishery in the 80's [@Murie1996] and moved to a limited-entry #fishery in 2001 [@IFMP2001]. Vessels without an observer have been required to retain a sample of 50/60 frozen sablefish for the department. The service provider Archipelago Marine Research (AMR) has #been responsible for the sablefish tag recovery program since the early 1990's, including the collection and biological sampling of tagged fish.

#   [@Serafy1996]    head measurements regression  on Red Drum fish
#   [@Park2007]      head measurements regression on Brown Croaker
#   [@Isermann2005]  head and mandible lengths regression on Walleye
#   [@Richardson2015] ratio of head height to eye diameter regression on New Zealand reef fishes

#  Head morphology showed sexual dimorphism as well [@mesa2005].

#  Morphometric characters  [@]
# The statistical relationship between total length (TL) and total body weight (W) of the fish was derived using the formula:
# log W = log a + b log TL  
# Where, W is the weight of fish (g); a is the intercept (constant); TL is
# the total length of fish (cm) and b is the regression coefficient (slope).

#first 137 fish measured (79 male and 58 female) 

```
\clearpage