# Introduction

  Biological samples of British Columbia (BC) sablefish (*Anoplopoma fimbria*) have been collected from fishery based voluntary catch sampling program since 1995 [@Haist2001].  Samples were processed by the Department of Fisheries and Oceans (DFO) port samplers and/or contracted service providers. In addition, whole tagged fish were recovered in commercial fisheries (trap, trawl, hook and line) at the point of landing via the dockside monitoring program (DMP) and sampled by Archipelago Marine Research (AMR) since the early 1990's.  These data provide a fishery dependent source of age and size composition data for the two-sex structured operating model of the coastal Management Strategy Evaluation (MSE) [@Cox2019].  
  
  The sablefish head-only catch sampling and tagging program began in 2018 in an effort to improve the number of returns from fishers, maintain the quality of the biological data and expand the spatial distribution of samples. Instead of returning the whole fish, commercial crew J-cut the fish as per commercial practice, view the gonads to determine sex, mark the sex with knife cuts on the operculum and store the head (and/or floy tag) for later sampling by DFO and AMR.
  
  Previous research on other fish species has accurately estimated lengths from head dimensions [@Serafy1996; @Park2007], head and mandible lengths [@Isermann2005], and head height to eye diameter ratio [@Richardson2015].  In this technical report we expand on previous research and describe the results of 1) the 2016 experimental study of cranial dimensions regressed against fork length; 2) the sampler defined ease of head measurement; 3) DNA sex detection methods; and 4) the compared consistency of the 2017 pilot study head measurements. 

```{r sampleCount} 

    pointdata    <-  read.csv(paste(path,'figure1.csv',sep=''),header=T)  # read from csv
    females      <-  pointdata[pointdata$SPECIMEN_SEX_DESC=='FEMALE',]
    males        <-  pointdata[pointdata$SPECIMEN_SEX_DESC=='MALE',]

```
  

```{r words_surplus}   

#ORDER OF EVENTS:
#1. 2016 sample sablefish on research surveys, collect bio data and DNA
#2. 2016 head measurements on shore PBS lab, evaluate measurements with 5 point scale
#3. 2016 develop dna sex id by PBS Molecular Genetics lab
#4. 2017 collect head samples on commercial vessel FOS TRIP 338773  Pacific Viking
#5  2017 measure head samples with 3 samplers to develop Index of Average Error
#6. 2017 use DNA to determine fisher sex accuracy

#The at-sea #observer program (ASOP) also collected biological data from the partial at-sea observer coverage (10% of sea days) on commercial trips from 2001 # through to 2005 [@IFMP2001], [@IFMP2004]. 

#In addition, biological samples have been processed by at-sea observers from the offshore seamount fishery that began as an experimental fishery in the 80's [@Murie1996] and moved to a limited-entry #fishery in 2001 [@IFMP2001]. Vessels without an observer have been required to retain a sample of 50/60 frozen sablefish for the department. The service provider Archipelago Marine Research (AMR) has #been responsible for the sablefish tag recovery program since the early 1990's, including the collection and biological sampling of tagged fish.

#   [@Serafy1996]   head measurements regression  on Red Drum fish
#   [@Park2007]  head measurements regression on Brown Croaker
#   [@Isermann2005] head and mandible lengths regression on Walleye
#   [@Richardson2015] ratio of head height to eye diameter regression on New Zealand reef fishes

#  Head morphology showed sexual dimorphism as well [@mesa2005].

#  Morphometric characters  [@]
# The statistical relationship between total length (TL) and total body weight (W) of the fish was derived using the formula:
# log W = log a + b log TL  
# Where, W is the weight of fish (g); a is the intercept (constant); TL is
# the total length of fish (cm) and b is the regression coefficient (slope).


 
```