# Introduction

  Biological samples of British Columbia (BC) Sablefish (*Anoplopoma fimbria*) from trap and hook and line fisheries have been collected from a fishery-based voluntary catch sampling program since 1995 [@Haist2001].  Prior to 2018, samples of whole fish were collected dockside by Fisheries and Oceans Canada (DFO) port samplers and/or contracted service providers via the dockside monitoring program (DMP). In addition, tagged fish were collected whole from commercial fisheries (trap, trawl, hook & line) at the point of landing, also by the dockside monitoring program. Biological data collected during catch sampling included fork length and sex. Otoliths were collected and archived for future ageing analyses.  These data provide a fishery-dependent source of age and size composition data for the two-sex age structured operating model used as part of the BC Management Strategy Evaluation (MSE) [@Cox2019, DFO 2020].
  
  Sablefish are typically processed at sea with a “J-cut” where the head is removed and the body cavity is scraped clean of all internal organs. Most of the directed commercial fishery catch is frozen at sea. A long standing concern with both the catch sampling and tag recovery sampling programs is that the larger fish are not submitted for biological sampling due to their high price per pound value.   Further, the whole fish collected for the sampling programs (prior to 2018) would take up valuable freezer space at sea, during transport and during storage on land.

  Between 2016 and 2017, DFO undertook research to evaluate the potential change to a 'head-only' catch sampling program for Sablefish trap and hook and line fisheries.  The key motivation for switching to a head-only sampling program was to increase the number and spatial distribution of fishery samples and to alleviate concerns around returns of the larger tagged fish  while maintaining the quality of biological data. Commercial crew J-cut the fish at-sea as per commercial practice, examine the gonads to determine sex, mark the sex with knife cuts on the operculum, and store the frozen head (and/or floy tag) for later sampling by science personal. Head-only sampling allows the commercial fishers to retain the full value of the captured fish and reduces the space and effort required to collect, store, transport, and sample the fish.

  Evaluating the potential success of a head-only sampling program for Sablefish required the development and testing of new methods. First, a method was required to estimate Sablefish fork length from head samples. Previous research on other fish species has shown that lengths can be accurately estimated from head dimensions [@Serafy1996; @Park2007], head and mandible lengths [@Isermann2005], and head height to eye diameter ratio [@Richardson2015], so we considered six different cranial measurement linked to these as a starting point for Sablefish.  Second, the accuracy of methods used by commercial fishing crew to identify and record sex needed to be assessed, which required the development of DNA analysis techniques for Sablefish gender assignment.

  In this technical report, we describe a research investigation in 2016 that collected Sablefish samples to: 1) identify cranial measurements that are reliable predictors of fork length for Sablefish; 2) identify cranial measurements that are practical to measure; and 3) develop DNA analysis techniques for gender assignment.  We also describe the fishery pilot study in 2017 to: 1) assess the ease of sample collection for commercial fishers; 2) determine the accuracy of fisher sex identification using DNA analysis; followed by 3) among-sampler measurements of each head morphometric.
  
  

```{r sampleCount} 

    pointdata    <-  read.csv(paste(path,'figure1.csv',sep=''),header=T)  # read from csv
    females      <-  pointdata[pointdata$SPECIMEN_SEX_DESC=='FEMALE',]
    males        <-  pointdata[pointdata$SPECIMEN_SEX_DESC=='MALE',]

```
  

```{r words_surplus}   

#ORDER OF EVENTS:
#1. 2016 sample Sablefish on research surveys, collect bio data and DNA
#2. 2016 head measurements on shore PBS lab, evaluate measurements with 5 point scale
#3. 2016 develop dna sex id by PBS Molecular Genetics Lab
#4. 2017 collect head samples on commercial vessel FOS TRIP 338773  Pacific Viking
#5  2017 measure head samples with 3 samplers to develop Index of Average Error
#6. 2017 use DNA to determine fisher sex accuracy

#The at-sea #observer program (ASOP) also collected biological data from the partial at-sea observer coverage (10% of sea days) on commercial trips from 2001 # through to 2005 [@IFMP2001], [@IFMP2004]. 

#In addition, biological samples have been processed by at-sea observers from the offshore seamount fishery that began as an experimental fishery in the 80's [@Murie1996] and moved to a limited-entry #fishery in 2001 [@IFMP2001]. Vessels without an observer have been required to retain a sample of 50/60 frozen Sablefish for the department. The service provider Archipelago Marine Research (AMR) has #been responsible for the Sablefish tag recovery program since the early 1990's, including the collection and biological sampling of tagged fish.

#   [@Serafy1996]    head measurements regression  on Red Drum fish
#   [@Park2007]      head measurements regression on Brown Croaker
#   [@Isermann2005]  head and mandible lengths regression on Walleye
#   [@Richardson2015] ratio of head height to eye diameter regression on New Zealand reef fishes

#  Head morphology showed sexual dimorphism as well [@mesa2005].

#  Morphometric characters  [@]
# The statistical relationship between total length (TL) and total body weight (W) of the fish was derived using the formula:
# log W = log a + b log TL  
# Where, W is the weight of fish (g); a is the intercept (constant); TL is
# the total length of fish (cm) and b is the regression coefficient (slope).

#first 137 fish measured (79 male and 58 female) 

```
\clearpage