# Results and Discussion

```{r fishData}

    fish         <-   read.csv(paste(path,"head_measurements.csv",sep=""), header = T)  # master data
    males        <-   fish[which(fish$SPECIMEN_SEX_DESC=='MALE'),]
    count.males  <-   length(males$SPECIMEN_ID)
    females      <-   fish[which(fish$SPECIMEN_SEX_DESC=='FEMALE'),]
    count.females<-   length(females$SPECIMEN_ID)
    fish.min     <-   min(fish$Fork_Length)
    fish.max     <-   max(fish$Fork_Length)
    fish.avg     <-   mean(fish$Fork_Length)
    
```

##  Experimental Study 2016

A total of 438 specimens comprising `r count.males` males and `r count.females` females were used for the study.  The smallest fork length of the collected specimens was `r fish.min` mm, the highest was `r fish.max` mm, and an average of `r fish.avg` (Table \@ref(tab:table3)).  


```{r yisFORKLENGTH}

    lmp <- function (modelobject) {                    #  p value function
           if (class(modelobject) != "lm") stop("Not an object of class 'lm' ")
                 f <- summary(modelobject)$fstatistic
                 p <- pf(f[1],f[2],f[3],lower.tail=F)
                 attributes(p) <- NULL
                 return(p)
    }

    lmslp <- function (modelobject) {                    #  slope (m) value function
             if (class(modelobject) != "lm") stop("Not an object of class 'lm' ")
                 slp <- signif(modelobject$coef[[2]], 5)
                 return(slp)
    }
    
    lmR <- function (modelobject) {                    #  r2 value function
             if (class(modelobject) != "lm") stop("Not an object of class 'lm' ")
                 r2 =  format(summary(modelobject)$r.squared,  digits = 3)
                 return(r2)
    }
    
    
    # y = Fork_Length, response variable
    options("scipen"=100, "digits"=3)
    

```    


The mean values of the predictor and response variables collected for five of the six head measurements (UJ, ED, IO, SL, PP, PH)(Table \@ref(tab:table2)).  The PH head was abandoned after 130 sablefish due to the time consuming and technical difficulties performing this measurement.

We found evidence of relationships between upper jaw length and fork length (p = `r lmp(lm(Fork_Length ~ Upper_jaw_length, data=hdUj))`) ; eye diameter and fork length (p = `r lmp(lm(Fork_Length ~ Eye_Diameter, data=hdEd))`); interorbital distance and fork length (p = `r lmp(lm(Fork_Length ~ InterOrbital_Distance, data=hdId))` ); upper snout length and fork length (p = `r lmp(lm(Fork_Length ~ Snout_length, data=hdSl))`); postorbital to preoperculum length and fork length (p = `r lmp(lm(Fork_Length ~ Postorbital_Preoperculum, data=hdPop))`); and postorbital head length and fork length (p = `r lmp(lm(Fork_Length ~ Post_orbital_Head_length, data=hdPo))`).

,  fork length, round weight, otoliths and DNA. 
Post orbital head length (Posterior inner edge of orbit to dorsal insertion of opercle) was also measured, but this was abandoned after 130 measurements, to save time, and because it was not possible to measure this on a number of the heads for a variety of reasons (opercula had been cut off from some heads, it was awkward to take longer measurements using the electronic calipers, and the end points of the measurement were difficult to define.  


## Estimation of Fork Length using Cranial Measurements




Given the ease of measurement, we suggest that Interorbital distance be used to predict sablefish fork lengths and weights (Table \@ref(tab:table3)). 



The estimated slope is `r lmslp(lm(Fork_Length ~ Upper_jaw_length, data=hdUj))` (SE `r coef(summary(lm(Fork_Length ~ Upper_jaw_length, data=hdUj)))[,"Std. Error"][2]`) units of fork length per unit of upper jaw length; the estimated slope is `r lmslp(lm(Fork_Length ~ Eye_Diameter, data=hdEd))` (SE `r  coef(summary(lm(Fork_Length ~ Eye_Diameter, data=hdEd)))[, "Std. Error"][2]`) units of fork length per unit of eye diameter; the estimated slope is `r lmslp(lm(Fork_Length ~ InterOrbital_Distance, data=hdId))` (SE `r coef(summary(lm(Fork_Length ~ InterOrbital_Distance, data=hdId)))[, "Std. Error"][2]`) units of fork length per unit of interorbital distance; the estimated slope is `r lmslp(lm(Fork_Length ~ Snout_length, data=hdSl))` (SE `r coef(summary(lm(Fork_Length ~ Snout_length, data=hdSl)))[, "Std. Error"][2]` units of fork length per unit of snout length; the estimated slope is `r lmslp(lm(Fork_Length ~ Postorbital_Preoperculum, data=hdPop))` (SE `r coef(summary(lm(Fork_Length ~ Postorbital_Preoperculum, data=hdPop)))[, "Std. Error"][2]`) units of fork length per unit of postorbital to preoperculum length; and the estimated slope is `r lmslp(lm(Fork_Length ~ Post_orbital_Head_length, data=hdPo))` (SE `r coef(summary(lm(Fork_Length ~ Post_orbital_Head_length, data=hdPo)))[, "Std. Error"][2]`) units of fork length per unit of postorbital head length.

##  Pilot Collection of Sablefish Heads as a Biological Sample

Heads were received by DFO in good condition (intact and not deformed), segregated by set, for measuring and otolith extraction.  Operculum cuts worked well to indicate sex

##  Repeatability of measurements between technicians

# Discussion

Routine biological sampling procedures have been modified so that commercial fisheries are now only returning heads, rather than entire fish.   

\clearpage