# Figures
```{r functionsForFigures}

    lm_eqn    <-   function(df,y,x, N){   # y = mx + b function  m=slope b=intercept
                        mod    <-  lm(y ~ x, df);
                        eq     <-  substitute(italic(y) == b + m %.% italic(x)*","~~italic(r)^2~"="~r2~", n ="~italic(n)~" ", 
                        list(b  =  format(unname(coef(mod)[1]),    digits = 2),
                             m  =  format(unname(coef(mod)[2]),    digits = 3),
                             r2 =  format(summary(mod)$r.squared,  digits = 3),
                             n  =  N))
                        as.character(as.expression(eq));
                        }
    
```

(ref:figure1) Sample locations in 2016 from the WCVI survey (GFBIO trip id 79190),  WCHG survey (GFBIO trip id 80378) and salmon survey (?).

```{r figure1, fig.cap='(ref:figure1)',warning=FALSE, echo=FALSE, message=FALSE, error= FALSE, width=5.9, height=8.5,fig.align='center'}

    png("C:/github/sablehead/figures/Figure1.png", units="px", width=1600, height=1800, res=150) # write png to file
    sql          <-   "select * from Head_Measurements_Report where SLAT > 0"  # head measurement data
    #pointdata    <-   GetSQLData(sql,"Sablefish")   # retrieve from seamount database
    #write.table(pointdata, file = paste(path,"figure1.csv",sep=''),row.names=FALSE, na="",col.names=TRUE,  sep=",") 
    pointdata    <-  read.csv(paste(path,'figure1.csv',sep=''),header=T)  # read from csv

    lon          <-   data.frame(pointdata$SLAT)
    lat          <-   data.frame(pointdata$SLON)
    spid         <-   data.frame(pointdata$SPECIMEN_ID)
    trip         <-   data.frame(pointdata$TRIP_ID)
    df           <-   as.data.frame(cbind(lon,lat,spid,trip))   # add year, lat, long, specimen_id to dataframe
                     
    canada       <-   readOGR(dsn = "C:/github/sablehead/storage",layer ="awscntry_geo", verbose = FALSE)  # open shapefile   
    shapef_can   <-   fortify(canada)    # fortify for ggplot require.
    points_df    <-   fortify(df)
    
    map          <-  ggplot() +
                     geom_polygon(data = shapef_can,  
                                  aes(x = long, y = lat, group = group), 
                                      fill="gray40",  
                                      size = .2) +
                     geom_point(data =   points_df,   aes(pointdata.SLON, pointdata.SLAT,  
                                                          fill=factor(pointdata.TRIP_ID),  size=0.7) , 
                                                          colour="gray50", shape=21, size=5) +            
                     theme_minimal()    +
                     guides(fill=FALSE) + 
                     guides(size=FALSE) + 
                     guides(fill=guide_legend(title="Trip id")) +
                     xlab("Longitude") + ylab("Latitude") + 
                     theme(  text = element_text(size=20),
                          plot.title      = element_blank(),
                          legend.position = c(.19, 0.35),
                          legend.justification = c("right", "top"),
                          legend.box.just = "right",
                          legend.margin = margin(6, 6, 6, 6)

                          )
   
    map_projected  <- map +   # reproject to make it look better
    coord_map()  +
    annotation_north_arrow(location = "bl", which_north = "true",  # north arrow
                           pad_x  = unit(3.75, "cm"),  
                           pad_y  = unit(4.5,  "cm"),
                           height = unit(2.5,  "cm"),
                           width  = unit(2.5,  "cm"),
                           style  = north_arrow_fancy_orienteering)
    
    map_projected        +
    annotation_scale(location = "bl",
                     pad_x = unit(1.0, "in"),  
                     pad_y = unit(1.0, "in"),
                     height = unit(0.5, "cm"),
                     width  = unit(5.95,"cm"),
                     text_cex = 1.0)   +
                     coord_sf(crs = 4326)

    while (!is.null(dev.list()))  dev.off()
    img <-   paste('C:/github/sablehead/figures/Figure1.png',sep="")   # -- retrieve png 
            knitr::include_graphics(img)
   
 
```

(ref:figure2) Scatterplot upper jaw vs fork length, measurements in millimeters.

```{r figure2, fig.cap='(ref:figure2)', results='asis',echo=FALSE, dpi=500, out.width = "400px", out.height ="290px", fig.align = "center"} 

     png("C:/github/sablehead/figures/figure2.png", units="px", width=1600, height=1200, res=300) # write png to file

     new_theme <- theme_bw() %+replace% 
                  theme(legend.position = c(0.84, 0.3))
     theme_set(new_theme)   # alter the bw theme so that legend has a position
     
     #  fit the regression line and get the results
     hd                     <-  hdUj                                        # Upper_jaw_length data
     n                      <-  length(hd$SPECIMEN_ID)                      # sample size
     hd.fit.outliers        <-  lm(Fork_Length ~ Upper_jaw_length, data=hd) # linear model
     hd$predicted           <-  predict(hd.fit.outliers)         # save the predicted values
     hd$residuals           <-  residuals(hd.fit.outliers)       # save the residual values
     out.liers              <-  abs(residuals(hd.fit.outliers)) > 100
     h                      <-  hd[out.liers,]
     h$indx                 <-  as.integer(rownames(h))    # label values considered outliers
     h$lbdist               <-  sign(h$residuals) * 20     # label distance
     
     ggplot(hd, aes(x = Upper_jaw_length, y = Fork_Length)) +
            ylab('Fork length (mm)')      +
            xlab("Upper jaw length (mm)") + 
            geom_smooth(method = "lm", se = FALSE, color = "grey") +                     # plot regression slope
            geom_segment(aes(xend = Upper_jaw_length, yend = predicted), alpha = .2) +   # alpha to fade lines
            geom_point(aes(color = residuals), size=1) +  
            scale_color_gradient2(low = "#d19c2f", mid = "#1ebecd", high = "purple") +     
            geom_point(aes(y = predicted), shape = 21, size=1) +  
            geom_text(data=h,x = h$Upper_jaw_length, y = h$Fork_Length + h$lbdist, 
                      label = h$SPECIMEN_ID, size=3.0) +                                   #  label outliers
            geom_text(x = 55, y = 1000, 
                      label = lm_eqn(hd, hd$Fork_Length, hd$Upper_jaw_length, n),  # y = mx + b label
                      parse = TRUE, size=4.2)

     while (!is.null(dev.list()))  dev.off()
     img <-   paste('C:/github/sablehead/figures/figure2.png',sep="")   # -- retrieve png 
              knitr::include_graphics(img)

```

(ref:figure3) Scatterplot eye diameter vs fork length, measurements in millimeters.

```{r figure3, fig.cap='(ref:figure3)', results='asis',echo=FALSE, dpi=500, out.width = "400px", out.height ="290px", fig.align = "center"} 

     png("C:/github/sablehead/figures/figure3.png", units="px", width=1600, height=1200, res=300) # write png to file

   #  fit the regression line and get the results
     hd                     <-  hdEd                                      # original data
     n                      <-  length(hd$SPECIMEN_ID)                    # number of specimens 
     hd.fit.outliers        <-  lm(Fork_Length ~ Eye_Diameter, data=hd)  # linear regression model #plot(hd.fit.outliers, which = 1, pch=21)
                                                                         # plot(hd$Eye_Diameter,hd$Fork_Length, xlim=c(0,20),ylim=c(0,400)) 
                                                                         # abline(hd.fit.outliers)
     hd.fit.outliersummary  <-  summary(hd.fit.outliers)               
     hd$predicted           <-  predict(hd.fit.outliers)   # save the predicted values
     hd$residuals           <-  residuals(hd.fit.outliers) # save the residual values
     o                      <-  abs(residuals(hd.fit.outliers)) > 100
     h                      <-  hd[o,]
     h$indx                 <-  as.integer(rownames(h))    # label values considered outliers
     h$lbdist               <-  sign(h$residuals) * 20
     
     ggplot(hd, aes(x = Eye_Diameter, y = Fork_Length)) +
            ylab('Fork length (mm)') +
            xlab("Eye diameter (mm)") + 
            geom_smooth(method = "lm", se = FALSE, color = "grey") +                # plot regression slope
            geom_segment(aes(xend = Eye_Diameter, yend = predicted), alpha = .2) +   # alpha to fade lines
            geom_point(aes(color = residuals), size=1)  +  
            scale_color_gradient2(low = "#d19c2f", mid = "#1ebecd", high = "purple") +    
            geom_point(aes(y = predicted), shape = 21, size=1)  +                   #   plot predicted white circles
            geom_text(data=h,x = h$Eye_Diameter, y = h$Fork_Length + h$lbdist, 
                      label = h$indx, size=3.0) +   # label outliers
                      #label= h$SPECIMEN_ID, size=3) +
            geom_text(x = 25, y = 1000, 
                      label = lm_eqn(hd, hd$Fork_Length, hd$Eye_Diameter, n),  # y = mx + b label
                      parse = TRUE, size=4.2)

     while (!is.null(dev.list()))  dev.off()
     img <-   paste('C:/github/sablehead/figures/figure3.png',sep="")   # -- retrieve png 
              knitr::include_graphics(img)

```

(ref:figure4) Scatterplot interorbital vs fork length.

```{r figure4, fig.cap='(ref:figure4)', results='asis',echo=FALSE, dpi=500, out.width = "400px", out.height ="290px", fig.align = "center"}

     png("C:/github/sablehead/figures/figure4.png", units="px", width=1600, height=1200, res=300) # write png to file

     #  fit the regression line and get the results
     hd                     <-  hdId                                       # original data
     n                      <-  length(hd$SPECIMEN_ID)                      # number of specimens 
     hd.fit.outliers        <-  lm(Fork_Length ~ InterOrbital_Distance, data=hd) # linear regression model #plot(hd.fit.outliers, which = 1, pch=21) 
     hd.fit.outliersummary  <-  summary(hd.fit.outliers)                    # summary

     hd$predicted          <-   predict(hd.fit.outliers)   # save the predicted values
     hd$residuals          <-   residuals(hd.fit.outliers) # save the residual values
     o                     <-   abs(residuals(hd.fit.outliers)) > 100
     h                     <-   hd[o,]
     h$indx                <-   as.integer(rownames(h))    # label values considered outliers
     h$lbdist              <-   sign(h$residuals) * 20
     
     ggplot(hd, aes(x = InterOrbital_Distance, y = Fork_Length)) +
            ylab('Fork length (mm)') +
            xlab("InterOrbital Distance (mm)") + 
            geom_smooth(method = "lm", se = FALSE, color = "grey") +                # plot regression slope
            geom_segment(aes(xend = InterOrbital_Distance, yend = predicted), alpha = .5) +   # alpha to fade lines
            geom_point(aes(color = residuals), size=1) +  
            scale_color_gradient2(low = "#d19c2f", mid = "#1ebecd", high = "purple") +   
            geom_point(aes(y = predicted), shape = 21, size=1) +                       #   plot predicted white circles
            geom_text(data=h,x = h$InterOrbital_Distance, y = h$Fork_Length + h$lbdist, 
                      label = h$indx, size=3.0) +   #label outliers
            geom_text(x = 45, y = 1000, 
                      label = lm_eqn(hd, hd$Fork_Length, hd$InterOrbital_Distance, n), 
                      parse = TRUE, size=4.2)

     while (!is.null(dev.list()))  dev.off()
     img <-   paste('C:/github/sablehead/figures/figure4.png',sep="")   # -- retrieve png 
              knitr::include_graphics(img)
```

(ref:figure5) Scatterplot snout length  vs fork length.

```{r figure5, fig.cap='(ref:figure5)', results='asis', dpi=500, out.width = "400px", out.height ="290px", fig.align = "center"}

png("C:/github/sablehead/figures/figure5.png",  units="px", width=1600, height=1200, res=300) # write png to file

   #  fit the regression line and get the results
     hd                     <-  hdSl                                     # snout length data
     n                      <-  length(hd$SPECIMEN_ID)                   # number of specimens 
     hd.fit.outliers        <-  lm(Fork_Length ~ Snout_length, data=hd)  # linear regression model #plot(hd.fit.outliers, which = 1, pch=21) 
     hd.fit.outliersummary  <-  summary(hd.fit.outliers)                 # summary

     hd$predicted           <-  predict(hd.fit.outliers)   # save the predicted values
     hd$residuals           <-  residuals(hd.fit.outliers) # save the residual values
     o                      <-  abs(residuals(hd.fit.outliers)) > 100
     h                      <-  hd[o,]
     h$indx                 <-  as.integer(rownames(h))    # label values considered outliers
     h$lbdist               <-  sign(h$residuals) * 20
     
     ggplot(hd, aes(x = Snout_length, y = Fork_Length)) +
            ylab('Fork length (mm)') +
            xlab("Snout length (mm)") + 
            geom_smooth(method = "lm", se = FALSE, color = "grey") +                # plot regression slope
            geom_segment(aes(xend = Snout_length, yend = predicted), alpha = .5) +   # alpha to fade lines
            geom_point(aes(color = residuals), size=1) +  
            scale_color_gradient2(low = "#d19c2f", mid = "#1ebecd", high = "purple") +     
            geom_point(aes(y = predicted), shape = 21, size=1) +               #   plot predicted white circles
            geom_text(data=h,x = h$Snout_length, y = h$Fork_Length + h$lbdist, 
                      label = h$indx, size=3.0) +   # label outliers
            geom_text(x = 45, y = 1000, 
                      label = lm_eqn(hd, hd$Fork_Length, hd$Snout_length, n), 
                      parse = TRUE, size=4.2)

     while (!is.null(dev.list()))  dev.off()
     img <-   paste('C:/github/sablehead/figures/figure5.png', sep="")   # -- retrieve png 
              knitr::include_graphics(img)
```

(ref:figure6) Scatterplot post orbital to preoperculum length vs fork length.

```{r figure6, fig.cap='(ref:figure6)', results='asis', dpi=500, out.width = "400px", out.height ="290px", fig.align = "center"}

     png("C:/github/sablehead/figures/figure6.png",units="px", width=1600, height=1200, res=300) # write png to file

   #  fit the regression line and get the results
     hd                     <-  hdPop                       # post orbital to preoperculum length data
     n                      <-  length(hd$SPECIMEN_ID)      # number of specimens 
     hd.fit.outliers        <-  lm(Fork_Length ~ Postorbital_Preoperculum, data=hd) # linear regression model #plot(hd.fit.outliers, which = 1, pch=21) 
     hd.fit.outliersummary  <-  summary(hd.fit.outliers)                    # summary

     hd$predicted       <- predict(hd.fit.outliers)   # save the predicted values
     hd$residuals       <- residuals(hd.fit.outliers) # save the residual values
     o                  <- abs(residuals(hd.fit.outliers)) > 100
     h                  <- hd[o,]
     h$indx             <- as.integer(rownames(h))    # label values considered outliers
     h$lbdist           <- sign(h$residuals) * 20
     
     ggplot(hd, aes(x = Postorbital_Preoperculum, y = Fork_Length)) +
            ylab('Fork length (mm)') +
            xlab("Postorbital to preoperculum (mm)") + 
            geom_smooth(method = "lm", se = FALSE, color = "grey") +                # plot regression slope
            geom_segment(aes(xend = Postorbital_Preoperculum, yend = predicted), alpha = .5) +   # alpha to fade lines
            geom_point(aes(color = residuals), size=1) +                            #   plot residuals
            scale_color_gradient2(low = "#d19c2f", mid = "#1ebecd", high = "purple") +    
            geom_point(aes(y = predicted), shape = 21, size=1) +                     #   plot predicted white circles
            geom_text(data=h,
                      x = h$Postorbital_Preoperculum, y = h$Fork_Length + h$lbdist, 
                      label = h$indx, size=3.0) +   # label outliers
            geom_text(x = 30, y = 1000, 
                      label = lm_eqn(hd, hd$Fork_Length, hd$Postorbital_Preoperculum, n), 
                      parse = TRUE, size=4.2) # y = mx + b label

     while (!is.null(dev.list()))  dev.off()
     img <-   paste('C:/github/sablehead/figures/figure6.png',sep="")   # -- retrieve png 
              knitr::include_graphics(img)
     
```

(ref:figure7) Scatterplot of post orbital length vs fork length.

```{r figure7, fig.cap='(ref:figure7)', results='asis',echo=FALSE, dpi=500, out.width = "400px", out.height ="290px", fig.align = "center"}

     png("C:/github/sablehead/figures/figure7.png", units="px", width=1600, height=1200, res=300) # write png to file

     #  fit the regression line and get the results
     hd                     <-  hdPo                                        # post orbital length data
     n                      <-  length(hd$SPECIMEN_ID)                      # number of specimens 
     hd.fit.outliers        <-  lm(Fork_Length ~ Post_orbital_Head_length, data=hd) # linear regression model 
     #plot(hd.fit.outliers, which = 1, pch=21)   # plot(hd$Post_orbital_Head_length,hd$Fork_Length)  # abline(hd.fit.outliers)
     hd.fit.outliersummary  <-  summary(hd.fit.outliers)                    # summary

     hd$predicted       <- predict(hd.fit.outliers)       #   save the predicted values
     hd$residuals       <- residuals(hd.fit.outliers)     #   save the residual values
     o                  <- abs(residuals(hd.fit.outliers)) > 100
     h                  <- hd[o,]
     h$indx             <- as.integer(rownames(h))       # create label values considered outliers
     h$lbdist           <- sign(h$residuals) * 20
     
     ggplot(hd, aes(x = Post_orbital_Head_length, y = Fork_Length)) +
            ylab('Fork length (mm)') +
            xlab("Postorbital head length (mm)") + 
            geom_smooth(method = "lm", se = FALSE, color = "grey") +                #   plot regression slope
            geom_segment(aes(xend = Post_orbital_Head_length, yend = predicted), alpha = .5) +  # alpha to fade lines
            geom_point(aes(color = residuals), size=1) +                          #   plot residuals
            scale_color_gradient2(low = "#d19c2f", mid = "#1ebecd", high = "purple") +   
            geom_point(aes(y = predicted), shape = 21, size=1) +                 #   plot predicted white circles
            geom_text(data=h,
                      x = h$Post_orbital_Head_length, y = h$Fork_Length + h$lbdist, 
                      label = h$indx, size=3.0) +   # label outliers
            geom_text(x = 75, y = 1100, 
                      label = lm_eqn(hd, hd$Fork_Length, hd$Post_orbital_Head_length, n), 
                      parse = TRUE, size=4.2)  # y = mx + b label

     while (!is.null(dev.list()))  dev.off()
     img <-   paste('C:/github/sablehead/figures/figure7.png',sep="")   # -- retrieve png 
              knitr::include_graphics(img)
              
```
\clearpage
