<!-- The following code should appear at the beginning of the first appendix.
(if you have one)
After that, all subsequent sections will be turned into appendices. -->

`r if(knitr:::is_latex_output()) '% begin csasdown appendix'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

\clearpage

# IMAGES OF THE SIX CRANIAL DIMENSION MEASUREMENTS.{#app:first-appendix}

A. Upper jaw measurement (UJ);  B. Eye diameter measurement (ED);  C. Interorbital distance (ID);  D. Snout length (SL);  E. Post orbital to preoperculum length measurement (PP); F. Post orbital head length (PO).


```{r appendixA}
 png(paste(graph_directory,"AppendixA.png", sep=""), units="px", width=1600, height=1800, res=150)# write png to file
    
   img         <- readPNG(paste(graph_directory,"AppendixAa.png", sep=""))
   g           <- rasterGrob(img, interpolate=TRUE)   # get image A. Upper jaw measurement
   img2        <- readPNG(paste(graph_directory,"AppendixAb.png", sep=""))
   g2          <- rasterGrob(img2, interpolate=TRUE)  # get image B. Eye diameter measurement
   img3        <- readPNG(paste(graph_directory,"AppendixAc.png", sep=""))
   g3          <- rasterGrob(img3, interpolate=TRUE)  # get image C. Interorbital measurement
   img4        <- readPNG(paste(graph_directory,"AppendixAd.png", sep=""))
   g4          <- rasterGrob(img4, interpolate=TRUE)  # get image D. Snout length 
   img5        <- readPNG(paste(graph_directory,"AppendixAe.png", sep=""))
   g5          <- rasterGrob(img5, interpolate=TRUE)  # get image E. Post orbital to preoperculum length measurement
   img6        <- readPNG(paste(graph_directory,"AppendixAf.png", sep=""))
   g6          <- rasterGrob(img6, interpolate=TRUE)  # get image F. Post orbital head length.   
 
   ggplot(data.frame(x = 1:3, y = 1:3), aes(x, y)) +
          geom_point(size = 0.00001, color="white") +

          annotation_custom(g,   xmin = 0.7,    xmax = 2.1,   ymin = 2.45,  ymax = 3.2)   +   
          #geom_text(x=0.99,  y=2.7, label="A.", size=0.6, color="white") + 
          annotation_custom(g2,  xmin = 1.87,   xmax = 3.2,   ymin = 2.45,  ymax = 3.2)   +   
          #geom_text(x=2.1,   y=2.7, label="B.", size=0.6, color="white") +  
          annotation_custom(g3,  xmin = 0.7,    xmax = 2.1,   ymin = 1.65,  ymax = 2.4)   +    
          #geom_text(x=0.99,  y=2.0, label="C.", size=0.6, color="white") + 
          annotation_custom(g4,  xmin = 1.87,   xmax = 3.2,   ymin = 1.65,  ymax = 2.4)   +   
          #geom_text(x=2.1,   y=2.0, label="D.", size=0.6, color="white") +  
          annotation_custom(g5,  xmin = 0.7,    xmax = 2.1,   ymin = 0.85,  ymax = 1.6)   +   
          #geom_text(x=0.99,  y=1.22,label="E.", size=0.6, color="white") +  
          annotation_custom(g6,  xmin = 1.87,   xmax = 3.35,  ymin = 0.85,  ymax = 1.6)   +   
          #geom_text(x=2.1,   y=1.22,label="F.", size=0.6, color="white") +
          theme(axis.title.x = element_text(colour = "white"),
          axis.title.y = element_text(colour = "white"),
          text=element_text(color="white"),
          axis.text=element_text(color="white"),
          panel.background = element_rect(fill = 'white', color = 'white'),
          axis.ticks.y = element_blank(),
          axis.ticks.x = element_blank()) 
         
   
     while (!is.null(dev.list()))  dev.off()
     img <-   paste(paste(graph_directory,"AppendixA.png", sep=""))   # -- retrieve png 
              knitr::include_graphics(img)
```

\clearpage

# SEX DETERMINATION BY OPERCULUM MARKING {#app:second-appendix}

Instructions for sex determinations and operculum knife cuts for sablefish males and females.

```{r AppendixB, results='asis'}
img <- paste(graph_directory,'AppendixB.png',sep='') 
      knitr::include_graphics(img)
```
\clearpage

<!-- At the end of your appendices add: -->
`r if(knitr:::is_latex_output()) '% end csasdown appendix'`
